Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
rewrite of grads

\subsection{Computation of the dual parameters for different losses}\todo{just a placeholder}
\label{app:losses}
As shown in \cref{eq:dual_param} in the main paper, our method relies on computation of the dual parameters. We can derive them in general for the family of exponential likelihoods, by rewriting the likelihood in the natural form,
\begin{equation}
 \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle,
\end{equation}
where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics which for all our likelihoods is simply $t(y)=y$, finally $f$ denotes the neural network output before the inverse link function. 
%given the loss functions we use $t(y) = y$. 
Then, taking the first and second derivatives of the loss in this form become:
\begin{equation}\label{eq:dual_param_app}
  -\nabla_{f} \log p(y_i \mid f) |_{f=f_i} =  A'(f_i) - y_i
  \quad \text{and} \quad
  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
\end{equation}
% The second derivative of the log partition function is easily calculated and
In this section, we provide the derivatives needed for the losses used in this work, \ie, the mean squared error (MSE) likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.

For regression, the negative log likelihood comes from the MSE, and for a single input it can be written as
\begin{equation}
	\ell(h(f), y) = \frac{1}{2} (y_i -f_i)^2,% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
\end{equation}
where the inverse link function is simply $h(f) = f$. Thus, the first and second derivatives are
\begin{equation}
	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} =  f_i - y_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1.
\end{equation}

@@

where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in [0, 1]$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function. Finally, we can write the first and second derivatives as follows

\begin{equation}
\begin{aligned}
	\nabla_f \ell(h(f), y_i)|_{f=f_i} &= - y_i + \left[ \textrm{Softmax}(\bm{f}) \right]_i \\
	\nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} &= \left[\textrm{Softmax}(\bm{f})\right]_i (1 - \left[\textrm{Softmax}(\bm{f})\right]_i).
\end{aligned}
\end{equation}

>>>>

\subsection{Computation of the dual parameters for different losses}
\label{app:losses}
As shown in \cref{eq:dual_param} in the main paper, our method relies on computation of the dual parameters. We can derive them in general for the family of exponential likelihoods, by rewriting the likelihood in the natural form,
\begin{equation}
 \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle,
\end{equation}
where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics which for all our likelihoods is simply $t(y)=y$, finally $f$ denotes the neural network output before the inverse link function. 
%given the loss functions we use $t(y) = y$. 
Then, taking the first and second derivatives of the loss in this form become:
\begin{equation}\label{eq:dual_param_app}
  \nabla_{f}  \ell(h(f), y_i) |_{f=f_i} =  A'(f_i) - y_i
  \quad \text{and} \quad
  \nabla^2_{f\!f} \ell(h(f), y_i)  |_{f=f_i} = A''(f_i).
\end{equation}
% The second derivative of the log partition function is easily calculated and
In this section, we provide the derivatives needed for the losses used in this work, \ie, the mean squared error (MSE) likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.

For regression, the negative log likelihood comes from the MSE, and for a single input it can be written as
\begin{equation}
	\ell(h(f_i), y_i) = \frac{1}{2} (y_i -f_i)^2,% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
\end{equation}
where the inverse link function is simply $h(f) = f$. Thus, the first and second derivatives are
\begin{equation}
	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} =  f_i - y_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1.
\end{equation}

@@
